Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-24 paper.tex
minor fixes

  \end{array}
  \]
  \caption{Definition of $applyCast$for \lazyD}
  \label{fig:applyCast-D-C}
\end{figure}

@@

\begin{figure}
  \[
  \begin{array}{lrcl}
  \stxrule{I}{Injectable types (\lazyD)}{
    \POOfun{T}{T} \mid \POOunit}
  \stxrule{I}{Injectable types (\lazyUD)}{
    \POOfun{\TOOdyn}{\TOOdyn} \mid \POOunit
  }
  \stxrule{c}{Coercions}{
    \ncInj{I} \mid
    \ncProj{I}{l} \mid
    \ncId \mid
    \ncFail{l} \mid
    \ncSeq{c}{c} \mid
    \ncFun{c}{c}
  }
  %% \stxrule{\bar{c}}{wrapper coercions}{  
  %%  \ncInj{I} \mid
  %%  \ncFun{\hat{c}}{\hat{c}} \mid
  %%  \ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
  %% }
% \stxrulecont{
%   \ncProd{\hat{c}}{\hat{c}} \mid
%   \ncSeq{\ncProd{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
%   \ncSum{\hat{c}}{\hat{c}} \mid
%   \ncSeq{\ncSum{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid  
% }
\stxrule{\hat{c}}{normal coercions}{
  \ncFun{\hat{c}}{\hat{c}} \mid
  \ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
  \ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
  \ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
  \ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
  \ncId \mid
  \ncProj{I}{l} \mid
  \ncInj{I} \mid
  \ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
  \ncFail{l} 
}
  %% \stxrule{\hat{c}}{normal coercions}{
  %%  \bar{c} \mid
  %%  \ncId \mid
  %%  \ncFail{l} \mid
  %%  \ncProj{I}{l} \mid
  %%  \ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
  %%  \ncSeq{\ncProj{I}{l}}{\ncInj{I}}
  %% }
  %% \stxrulecont{
  %%  \ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
  %%  \ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
  %% }
  \end{array}
  \]
  \caption{Syntax of coercions and normal forms}
  \label{fig:normal-coercion}
\end{figure}

@@

Coercions come with a reduction relation so it is natural to ask about
their normal forms. \figref{fig:normal-coercion} defines the syntax of
coercions in normal form, written $\hat{c}$. Conceptually, a coercion
in normal form has three parts, all of which are optional.  It may
start with a projection $I?^l$, followed by a function coercion, and
then concluded with an injection $I!$ or a failure $\bot^l$. While
this is a simple idea, there are 10 clauses in the definition for
$\hat{c}$!

@@

\section{Definition of Hypercoercions} \label{sec:hypercoercion-definition}

>>>>

  \end{array}
  \]
  \caption{Definition of $applyCast$ for \lazyD}
  \label{fig:applyCast-D-C}
\end{figure}

@@

\begin{figure}
  \[
  \begin{array}{lrcl}
  \stxrule{I}{Injectable types (\lazyD)}{
    \POOfun{T}{T} \mid \POOunit}
  \stxrule{I}{Injectable types (\lazyUD)}{
    \POOfun{\TOOdyn}{\TOOdyn} \mid \POOunit
  }
  \stxrule{c}{Coercions}{
    \ncInj{I} \mid
    \ncProj{I}{l} \mid
    \ncId \mid
    \ncFail{l} \mid
    \ncSeq{c}{c} \mid
    \ncFun{c}{c}
  }
\stxrule{\hat{c}}{normal coercions}{
  \ncFun{\hat{c}}{\hat{c}} \mid
  \ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
  \ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
  \ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
  \ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
  \ncId \mid
  \ncProj{I}{l} \mid
  \ncInj{I} \mid
  \ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
  \ncFail{l} 
}
  \end{array}
  \]
  \caption{Syntax of coercions and normal forms}
  \label{fig:normal-coercion}
\end{figure}

@@

Coercions come with a reduction relation so it is natural to ask about
their normal forms. \figref{fig:normal-coercion} defines the syntax of
coercion in normal form, written $\hat{c}$. Conceptually, a coercion
in normal form has three parts, all of which are optional.  It may
start with a projection $I?^l$, followed by a function coercion, and
then concluded with an injection $I!$ or a failure $\bot^l$. While
this is a simple idea, there are 10 clauses in the definition for
$\hat{c}$!

@@

\section{Definition of Hypercoercions} \label{sec:hypercoercion-definition}
\todo[inline]{
The figures of applyCast for hypercoercions is before coercions, even before 
the syntax definition of hypercoercions! -KC
}
